---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggsample

<!-- badges: start -->
<!-- badges: end -->

The goal of ggsample provide functions for sampling.  The facet_* functions could be especially statistical education in helping visualize hypothetical scenarios (like sampling from known population) or demonstrating resampling techniques.  The facet_* functions mostly borrow from the ggplot2 extension vignette [(extending existing facet function)](https://github.com/tidyverse/ggplot2/blob/5f518d02af27160ab98fed736a472321d72d10d2/vignettes/extending-ggplot2.Rmd#L1028). But a seed setting move has been added such that the layers in each facet are looking at the same sampling frame; i.e. geom_smooth() will be acting on the same data as geom_point() points   This which didn't seem to be the case when only using the vignette strategy as-is. The functions are:

- `facet_sample()`
- `facet_sample_prop()`
- `facet_bootstrap()`
- `facet_scramble()`

There are also some geom experiments, which I think might be less useful.

## Installation

<!-- You can install the released version of ggsample from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("ggsample") -->
<!-- ``` -->

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("EvaMaeRey/ggsample")
```
## Examples

Below we display 9 panels with different a sample of 16 (n_facets default) observations taken.

```{r example, eval = T}
library(ggplot2)
library(ggsample)

# facet_sample
ggplot(data = mtcars) +
   aes(x = wt) +
   aes(y = mpg) +
   facet_sample(n_sampled = 10) +
   geom_point(alpha = .5) +
   geom_smooth(method = lm, se = F)
```

We can also sample by specifying a proportion with facet_sample_prop().

```{r, eval = T}
# facet_sample_prop
ggplot(data = mtcars) +
   aes(x = wt) +
   aes(y = mpg) +
   facet_sample_prop(prop = .2, 
                n_facets = 9) +
   geom_point(alpha = .5) +
   geom_smooth(method = lm, se = F)
```


We can also bootstrap taking a sample of nrow(data) with replacement via facet_bootstrap().


```{r , eval = T}
# facet_bootstrap
ggplot(data = mtcars) +
   aes(x = wt) +
   aes(y = mpg) +
   facet_bootstrap() +
   geom_count(alpha = .2) +
   geom_smooth(method = lm, se = F) 
```

Looking at disassociated data (variables in a dataset are randomly reordered) is also possible via facet_scramble().

```{r, eval = T}
# facet_scramble
ggplot(data = mtcars) +
   aes(x = wt) +
   aes(y = mpg) +
   facet_scramble(n_facets = 9) +
   geom_point(alpha = .2) +
   geom_smooth(method = lm, se = F) 
```

# Simulating reality: single sample realization with `facet_*(n_facets = 1)`

You can use `facet_*(n_facets = 1)` to see a single realization.  In a classroom setting you can re-execute code to see multiple realizations one at a time.  last_plot() does *not* produce a fresh sample; but overriding facet_sample does work.

I wonder if some helpers might be nice like facet_sample_once() for this special case. 


```{r}
ggplot(data = mtcars) +
   aes(x = wt) +
   aes(y = mpg) +
   facet_sample(n_sampled = 10,
                n_facets = 1) +
   geom_point(alpha = .5) +
   geom_smooth(method = lm, se = F)

# replace facet declaration
last_plot() + facet_sample(n_sampled = 10, n_facets = 1)
```



# Functions internals...


Here, you'll see a lot of cloned code from the ggplot2 extension vignette!   https://github.com/tidyverse/ggplot2/blob/5f518d02af27160ab98fed736a472321d72d10d2/vignettes/extending-ggplot2.Rmd#L1028  The small contribution made here is the seed parameter which, ensures that layers are displayed based on the same sample (geom_smooth reflects the same data as geom_point) which seems to have worked. 

There is a lot of repetition in what's below and it might be good to try to consolidate some of this at some point. 

```{r a_compute_layout_sample}
compute_layout_sample <- function(data, params) {
  
      id     <- seq_len(params$n)
      dims   <- wrap_dims(params$n, params$nrow, params$ncol)
      layout <- data.frame(PANEL = factor(id))

      if (params$as.table) { layout$ROW <- as.integer((id - 1L) %/% dims[2] + 1L)
      } else {               layout$ROW <- as.integer(dims[1] - (id - 1L) %/% dims[2]) }
      
                             layout$COL <- as.integer((id - 1L) %% dims[2] + 1L)

      layout <- layout[order(layout$PANEL), , drop = FALSE]
                                  
      rownames(layout) <- NULL

      # Add scale identification
      layout$SCALE_X <- if (params$free$x) id else 1L
      layout$SCALE_Y <- if (params$free$y) id else 1L

      cbind(layout, .bootstrap = id)
      
      }
```


```{r facet_sample}


map_data_sample <- function(data, layout, params) {
  
      if (is.null(data) || nrow(data) == 0) {return(cbind(data, PANEL = integer(0)))}
                                  
      set.seed(params$seed) # adding this
                                  
      n_sampled <- params$n_sampled
      
      new_data <- lapply(seq_len(params$n), function(i) {
        cbind(data[sample(nrow(data), n_sampled), , drop = FALSE], PANEL = i)
                                  })
      do.call(rbind, new_data)
                                
      }

FacetSample <- ggplot2::ggproto(
  `_class`   = "FacetSample", 
  `_inherit` = ggplot2::FacetWrap,
  compute_layout = compute_layout_sample,
  map_data = map_data_sample
)

#' Title
#'
#' @param n_facets number of facets
#' @param nrow how many rows for facet grid
#' @param ncol how many columns for facet grid
#' @param scales should x and y scales be determined independently for facets
#' @param shrink not sure what shrink does
#' @param strip.position where facet label should go
#' @param n_sampled sample size
#' @param seed randomization start point
#'
#' @return a ggplot2 facet specification
#' @export
#'
#' @examples
#' # mean from samples
#' library(ggplot2)
#' ggplot(data = mtcars) +
#'    aes(x = wt) +
#'    aes(y = mpg) +
#'    facet_sample(n_sampled = 10, 
#'                 n_facets = 9,
#'                 nrow = 3) +
#'    geom_point(alpha = .5) +
#'    geom_smooth(method = lm, se = F)
#'   labs(subtitle = "Depending on our particular random sample...") 
facet_sample <- function(n_facets = 16, n_sampled = 5, nrow = NULL, ncol = NULL,
                         scales = "fixed", shrink = TRUE, strip.position = "top",
                         seed = sample(2000:3000, 1)) {

  facet <- ggplot2::facet_wrap(~.bootstrap, nrow = nrow, ncol = ncol, scales = scales,
                               shrink = shrink, strip.position = strip.position)
  
  facet$params$n <- n_facets
  facet$params$n_sampled <- n_sampled
  facet$params$seed <- seed

  ggplot2::ggproto(`_class` = NULL, 
                   `_inherit` = FacetSample,
                   shrink = shrink,
                   params = facet$params)
  
}



```

### try it out 

```{r}
library(ggplot2)
ggplot(data = mtcars) +
   aes(x = wt) +
   aes(y = mpg) +
   facet_sample(n_sampled = 10, 
                n_facets = 9,
                nrow = 3) +
   geom_point(alpha = .5) +
   geom_smooth(method = lm, se = F)

```



### facet_sample_prop()

```{r facet_sample_prop}
#' Title
#'
#' @inheritParams facet_sample
#' @param prop numeric proportion to sample, defaults to .2
#'
#' @return
#' @export
#'
#' @examples
#' set.seed(1323)
#' library(ggplot2)
#' ggplot(data = cars) +
#'   aes(x = speed) +
#'   aes(y = dist) +
#'   geom_point(color = "olivedrab4") +
#'   geom_smooth(method = lm, se = FALSE) +
#'   facet_sample_prop() +
#'   labs(title = "Random Sample, 20% of population")
facet_sample_prop <- function(n_facets = 9, prop = 0.2, nrow = NULL, ncol = NULL,
                            scales = "fixed", shrink = TRUE, strip.position = "top",
                         seed = sample(2000:3000, 1)) {

  facet <- ggplot2::facet_wrap(~.bootstrap, nrow = nrow, ncol = ncol, scales = scales,
                      shrink = shrink, strip.position = strip.position)
  
  facet$params$n <- n_facets
  facet$params$prop <- prop
  facet$params$seed <- seed

  ggplot2::ggproto(NULL, FacetSampleProp,
          shrink = shrink,
          params = facet$params
  )
}


map_data_sample_prop <- function(data, layout, params) {
                            if (is.null(data) || nrow(data) == 0) {
                              return(cbind(data, PANEL = integer(0)))
                            }
                            set.seed(params$seed)
                            n_samples <- round(nrow(data) * params$prop)
                            new_data <- lapply(seq_len(params$n), function(i) {
                              cbind(data[sample(nrow(data), n_samples), , drop = FALSE], PANEL = i)
                            })
                            do.call(rbind, new_data)
                          }

FacetSampleProp <- ggplot2::ggproto("FacetSampleProp", ggplot2::FacetWrap,
                          compute_layout = compute_layout_sample,
                          map_data = map_data_sample_prop
)
```

### Try it out...

```{r}
# facet_sample_prop
ggplot(data = mtcars) +
   aes(x = wt) +
   aes(y = mpg) +
   facet_sample_prop(prop = .1, 
                n_facets = 9,
                nrow = 3) +
   geom_point(alpha = .5) +
   geom_smooth(method = lm, se = F)
```




### facet_bootstrap()

```{r facet_bootstrap}
#' Resample with replacement
#'
#' @inheritParams facet_sample_prop
#'
#' @return
#' @export
#'
#' @examples
#' library(ggplot2)
#' set.seed(1323)
#' ggplot(data = cars) +
#'   aes(x = speed) +
#'   aes(y = dist) +
#'   geom_count(alpha = .5) +
#'   facet_bootstrap(n_facets = 1) +
#'   facet_bootstrap(n_facets = 2) +
#'   facet_bootstrap(n_facets = 3) +
#'   ggxmean::geom_lm() +
#'   ggxmean::geom_lm_formula() +
#'   facet_bootstrap(n_facets = 15)
facet_bootstrap <- function(n_facets = 9, prop = 1, nrow = NULL, ncol = NULL,
                            scales = "fixed", shrink = TRUE, strip.position = "top",
                            seed = sample(2000:3000, 1)) {

  facet <- ggplot2::facet_wrap(~.bootstrap, nrow = nrow, ncol = ncol, scales = scales,
                      shrink = shrink, strip.position = strip.position)
  facet$params$n <- n_facets
  facet$params$prop <- prop
  facet$params$seed <- seed
  ggplot2::ggproto(NULL, FacetBootstrap,
          shrink = shrink,
          params = facet$params
  )
}

map_data_bootstrap <- function(data, layout, params) {
                            if (is.null(data) || nrow(data) == 0) {
                              return(cbind(data, PANEL = integer(0)))
                            }
                            n_samples <- round(nrow(data) * params$prop)
                            set.seed(params$seed)
                            new_data <- lapply(seq_len(params$n), function(i) {
                              cbind(data[sample(nrow(data), n_samples, replace = T), , drop = FALSE], PANEL = i)
                            })
                            do.call(rbind, new_data)
                          }

FacetBootstrap <- ggplot2::ggproto("FacetBootstrap", ggplot2::FacetWrap,
                          compute_layout = compute_layout_sample,
                          map_data = map_data_bootstrap
)



```

### Test it out...

```{r}

# facet_bootstrap
ggplot(data = mtcars) +
   aes(x = wt) +
   aes(y = mpg) +
   facet_bootstrap(n_facets = 9,
                   nrow = 3) +
   geom_count(alpha = .2) +
   geom_smooth(method = lm, se = F) 
```


### facet_scramble

```{r facet_scramble}
#' Title
#'
#' @inheritParams facet_sample_prop
#'
#' @return
#' @export
#'
#' @examples
#' library(ggplot2)
#' set.seed(232)
#' ggplot(data = cars) +
#'   aes(x = speed) +
#'   aes(y = dist) +
#'   geom_rug() +
#'   geom_point(color = "springgreen4",
#'            alpha = .75) +
#'   ggxmean:::geom_corrlabel() +
#'   labs(subtitle = "Pearson Correlation Coefficient(s)") +
#'   facet_scramble(n_facets = 1) +
#'   labs(title = "Disassociating variables") +
#'   facet_scramble(n_facets = 2) +
#'   facet_scramble(n_facets = 3) +
#'   facet_scramble(n_facets = 12) +
#'   ggxmean::geom_lm()
#'
facet_scramble <- function(n_facets = 9, prop = 1, nrow = NULL, ncol = NULL,
                            scales = "fixed", shrink = TRUE, strip.position = "top",
                           seed = sample(2000:3000, 1)) {

  facet <- ggplot2::facet_wrap(~.bootstrap, nrow = nrow, ncol = ncol, scales = scales,
                      shrink = shrink, strip.position = strip.position)
  facet$params$n <- n_facets
  facet$params$seed <- seed
  facet$params$prop <- prop
  ggplot2::ggproto(NULL, FacetScramble,
          shrink = shrink,
          params = facet$params
  )
}


shuffle <- function(dat){

  for(i in 1:ncol(dat)){
    dat[,i] = sample(dat[,i])
  }

  dat

}

map_data_shuffle <- function(data, layout, params) {
                            if (is.null(data) || nrow(data) == 0) {
                              return(cbind(data, PANEL = integer(0)))
                            }
                            set.seed(params$seed)
                            # n_samples <- round(nrow(data) * params$prop)
                            new_data <- lapply(seq_len(params$n), function(i) {
                              # data$y <- sample(data$y)

                              cbind(shuffle(data), PANEL = i)
                            })
                            do.call(rbind, new_data)
                          }

FacetScramble <- ggplot2::ggproto("FacetScramble", ggplot2::FacetWrap,
                          compute_layout = compute_layout_sample,
                          map_data = map_data_shuffle
)

```

### try it

```{r}
# facet_scramble
ggplot(data = mtcars) +
   aes(x = wt) +
   aes(y = mpg) +
   facet_scramble(n_facets = 9,
                  nrow = 3) +
   geom_point(alpha = .2) +
   geom_smooth(method = lm, se = F) 
```



## Send to R dir


```{r}
library(tidyverse)
knitrExtra:::chunk_to_r("a_compute_layout_sample")
knitrExtra:::chunk_to_r("facet_sample")
knitrExtra:::chunk_to_r("facet_sample_prop")
knitrExtra:::chunk_to_r("facet_bootstrap")
knitrExtra:::chunk_to_r("facet_scramble")
```
