---
title: ggsample
subtitle: ""
author: "Exploded Examples"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: [default, hygge, ninjutsu]
    nature:
      ratio: 16:9
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, echo = F}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F, fig.height = 6, comment = "")
options(knitr.duplicate.label = "allow")
library(ggsample)
```


---

`r flipbookr::chunk_reveal('facet_bootstrap_1', title = '### facet_bootstrap')`

```{r facet_bootstrap_1, include = F}
library(ggplot2)
set.seed(1323)
ggplot(data = cars) +
  aes(x = speed) +
  aes(y = dist) +
  geom_point(color = "olivedrab4",
             alpha = .5) +
  geom_count(alpha = .2) +
  facet_bootstrap(n = 12) +
  geom_smooth(method = lm, se = FALSE)
```



---

`r flipbookr::chunk_reveal('facet_sample_2', title = '### facet_sample')`

```{r facet_sample_2, include = F}
set.seed(1323)
library(ggplot2)
ggplot(data = cars) +
  aes(x = speed) +
  aes(y = dist) +
  geom_point(color = "olivedrab4") +
  geom_smooth(method = lm,
              se = FALSE) +
  labs(caption = "Population are observations from cars correlation study dataset") +
  facet_sample(n_sampled = 8) +
  labs(title = "16 draws, random sample of 8 observations from the population") +
  labs(subtitle = "Depending on our particular random sample, slopes are flatter or steepernand intercepts vary")
```



---

`r flipbookr::chunk_reveal('facet_sample_prop_3', title = '### facet_sample_prop')`

```{r facet_sample_prop_3, include = F}
set.seed(1323)
library(ggplot2)
ggplot(data = cars) +
  aes(x = speed) +
  aes(y = dist) +
  geom_point(color = "olivedrab4") +
  geom_smooth(method = lm, se = FALSE) +
  facet_sample_prop() +
  labs(title = "Random Sample, 20% of population")
```



---

`r flipbookr::chunk_reveal('facet_scramble_4', title = '### facet_scramble')`

```{r facet_scramble_4, include = F}
library(ggplot2)
ggplot(data = cars) +
  aes(x = speed) +
  aes(y = dist) +
  geom_point(color = "springgreen4",
           alpha = .75) +
  facet_scramble(n = 12) +
  geom_smooth(method = lm, se = FALSE) +
  labs(title = "Disassociating variables")
```



---

`r flipbookr::chunk_reveal('geom_lm_sample_5', title = '### geom_lm_sample')`

```{r geom_lm_sample_5, include = F}
my_seed <- sample(1:100, 1)
library(ggplot2)
ggplot(data = cars) +
  aes(x = speed, y = dist) +
  geom_point() +
  geom_smooth(method = lm,
             se = FALSE) +
   geom_point_sample(color = "red",
                     seed = my_seed) +
   geom_lm_sample(color = "red",
                  seed = my_seed)
```



---

`r flipbookr::chunk_reveal('geom_point_sample_6', title = '### geom_point_sample')`

```{r geom_point_sample_6, include = F}
# using the function
set.seed(92389)
library(ggplot2)
ggplot(data = cars) +
 aes(x = speed, y = dist) +
 geom_point() +
 geom_point_sample(color = "red") +
 geom_point_sample(color = "green",
                   sample_size = 5) +
 geom_point_sample(sample_size = 2,
                   color = "blue")
```


